Off the beaten path: \\ Gaia reveals GD-1 stars outside of the main stream

### 2018-06-21 paper/gd1.tex
polygon

As a first selection of GD-1 member stars, we choose stars \changes{that lie in the orange polygon in proper motions (top right panel of \figurename~\ref{fig:selection}; approximately bounded by the rectangle
$-9 < \mu_{\phi_1, \odot} < -4.5~\masyr$ and $-1.7 < \mu_{\phi_2, \odot} <
1~\masyr$).}
\figurename~\ref{fig:selection} (top left) shows all stars that pass the
selection, plotted in the GD-1 coordinate system.
The stream is already identifiable as the overdensity of stars around $\phi_2 =
0$ between longitudes $-60^\circ \lesssim \phi_1 \lesssim 0^\circ$.

>>>>

As a first selection of GD-1 member stars, we choose stars \changes{that lie in a polygon in proper motions (orange shaded polygon in top right panel of \figurename~\ref{fig:selection}; approximately bounded by the rectangle
$-9 < \mu_{\phi_1, \odot} < -4.5~\masyr$ and $-1.7 < \mu_{\phi_2, \odot} <
1~\masyr$).}
\figurename~\ref{fig:selection} (top left) shows all stars that pass the
selection, plotted in the GD-1 coordinate system.
The stream is already identifiable as the overdensity of stars around $\phi_2 =
0$ between longitudes $-60^\circ \lesssim \phi_1 \lesssim 0^\circ$.
